---
title: "Assignment4"
output: word_document
---

Question 1
(a)
Equation below:





(b)
```{r , echo=FALSE}
data<-read.csv('/Users/will/Documents/GitHub/STAT-332-Experimental-Design/Assignment_Data/a4q1data.csv')
attach(data)
interaction.plot(Price,Inflation,Tire.Wear.Out,type='l',xlab ='Price', ylab='Mean of Tire Wear Out',main='Interaction Plot of Price and Inflation',legend='TRUE')
```

(c)(i)Yes, there is a significant difference between the factor ‘price’ so there is significant difference between the treatments

```{r , echo=TRUE}
data<-read.csv('/Users/will/Documents/GitHub/STAT-332-Experimental-Design/Assignment_Data/a4q1data.csv')
attach(data)
model<- lm(Tire.Wear.Out~as.factor(Treatment))
summary(aov(model))
```

(ii)	The interaction parameters are not significantly different from zero.
```{r , echo=TRUE}
model<-lm(Tire.Wear.Out~as.factor(Price)+as.factor(Inflation)+as.factor(Price)*as.factor(Inflation))
summary(aov(model))
```

(d)
```{r , echo=TRUE}
with(data, tapply(Tire.Wear.Out, list(Price,Inflation), mean))
pt(0.1166,20)
```


Question 2

(a)Each soap formulation should be randomly assigned to each treatment




(b)



(c)
```{r , echo=TRUE}
data<-read.csv('/Users/will/Documents/GitHub/STAT-332-Experimental-Design/Assignment_Data/Soap2.csv')
attach(data)
model<-lm(Process.capability~as.factor(Moisture.content)+as.factor(Coolant.Temperature)+as.factor(Mixing.Temperature)*as.factor(Coolant.Temperature))
summary(aov(model))
```
(i) There is no significant difference among the treatments
(ii)	There are no interaction parameters significantly different from zero

